Sketch Recognition and Understanding

### 2009-09-26 trunk/draft/Results.tex
after approval of dr. samia

	\caption[Symbols in EL-DB]{Example of Electrical Symbols}
	\label{fig:ElectSet}
\end{figure}
\begin{table}
\begin{center}
\scalebox{0.9}{
 \begin{tabular}{|p{5cm}|p{2.5cm}|p{2.5cm}|p{2.5cm}|}
 \hline
 & Hs-DB &  EL-DB & LD-DB \\ \hline
No of samples  &  7791 & 2764 & 1859 \\ \hline
No of categories  & 13 & 15 & 8 \\ \hline
Avg. Samples per Category& 600 & 184 & 232 \\\hline 
No of users  & 16 & 7 & 7 \\  \hline
Balanced & Yes&No & No \\ \hline
Splits  & 5 random splits  & 5 random splits  & 5 random splits  \\ \hline
Examples & Figure \ref{fig:symbolSet}  & Figure \ref{fig:ElectSet}  & Figure \ref{fig:LogicSet}   \\ \hline
\end{tabular}
}
\caption[Datasets Comparisons]{Datasets Comparisons} 
\label{tab:datasets}

@@

 \begin{table*}
	\centering
	%\small
%	\scalebox{0.7}{
		%	\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|c|c|c|}\hline 
	\scalebox{0.5}{
		\begin{tabular}{|p{2cm}|c|c|c|c|c|c|c|c|c|c|c|c|c||p{2cm}|c|c|c|c|p{2cm}|}\hline 
		Categorie / classified as ==$>$	&ellipse	&heart	&trapezoid	&pentagon	&arch	&hexagon	&square	&triangle	&cube	&cylinder	&parallelogram	&moon	&callout	&Number of samples per class	&TP count	&FP count	&Fn	&Precision	&Recall ( TP rate )\\ \hline 
ellipse	&150	&20	&0	&0	&0	&5	&1	&0	&0	&0	&0	&1	&0	&152	&150	&27	&2	&0.8474	&0.9868\\ \hline 
heart	&2	&130	&0	&1	&10	&1	&1	&0	&0	&0	&1	&4	&0	&152	&130	&20	&22	&0.86666	&0.8552\\ \hline 
trapezoid	&0	&1	&147	&5	&1	&0	&1	&3	&2	&0	&37	&0	&0	&150	&147	&50	&3	&0.7461	&0.98\\ \hline 
pentagon	&0	&0	&1	&139	&0	&7	&0	&0	&0	&0	&1	&0	&0	&152	&139	&9	&13	&0.9391	&0.91447\\ \hline 
arch	&0	&0	&1	&1	&125	&0	&4	&0	&3	&0	&0	&15	&1	&151	&125	&25	&26	&0.83333	&0.82781\\ \hline 
hexagon	&0	&0	&0	&2	&0	&135	&0	&0	&0	&0	&0	&0	&0	&151	&135	&2	&16	&0.9854	&0.89403\\ \hline 
square	&0	&0	&0	&0	&0	&0	&138	&0	&0	&0	&0	&1	&0	&151	&138	&1	&13	&0.9928	&0.91390\\ \hline 
triangle	&0	&0	&1	&2	&5	&0	&1	&148	&0	&0	&4	&7	&0	&151	&148	&20	&3	&0.88095	&0.98013\\ \hline 
cube	&0	&0	&0	&1	&0	&0	&0	&0	&146	&5	&0	&0	&0	&153	&146	&6	&7	&0.96052	&0.95424\\ \hline  
cylinder	&0	&0	&0	&1	&0	&1	&0	&0	&0	&147	&0	&0	&0	&152	&147	&2	&5	&0.98657	&0.967105\\ \hline 
parallelogram	&0	&0	&0	&0	&0	&0	&2	&0	&2	&0	&107	&0	&0	&150	&107	&4	&43	&0.963	&0.71333\\  \hline 
moon	&0	&1	&0	&0	&10	&2	&3	&0	&0	&0	&0	&125	&5	&153	&125	&21	&28	&0.8561	&0.8169\\ \hline  
callout	&0	&0	&0	&0	&0	&0	&0	&0	&0	&0	&0	&0	&145	&151	&145	&0	&6	&1	&0.9602\\  \hline  
% Categories 	&ellipse	&heart	&trapezoid	&pentagon	&arch	&hexagon	&square	&triangle	&cube	&cylinder	&parallelogram	&moon	&callout\\ \hline 
%ellipse	&150	&20	&0	&0	&0	&5	&1	&0	&0	&0	&0	&1	&0\\  \hline 
%heart	&2	&130	&0	&1	&10	&1	&1	&0	&0	&0	&1	&4	&0\\  \hline 
%trapezoid	&0	&1	&147	&5	&1	&0	&1	&3	&2	&0	&37	&0	&0\\  \hline 
%pentagon	&0	&0	&1	&139	&0	&7	&0	&0	&0	&0	&1	&0	&0\\   \hline 
%arch	&0	&0	&1	&1	&125	&0	&4	&0	&3	&0	&0	&15	&1\\   \hline 
%hexagon	&0	&0	&0	&2	&0	&135	&0	&0	&0	&0	&0	&0	&0\\  \hline 
%square	&0	&0	&0	&0	&0	&0	&138	&0	&0	&0	&0	&1	&0\\   \hline 
%triangle	&0	&0	&1	&2	&5	&0	&1	&148	&0	&0	&4	&7	&0\\  \hline 
%cube	&0	&0	&0	&1	&0	&0	&0	&0	&146	&5	&0	&0	&0\\   \hline 
%cylinder	&0	&0	&0	&1	&0	&1	&0	&0	&0	&147	&0	&0	&0\\  \hline 
%parallelogram	&0	&0	&0	&0	&0	&0	&2	&0	&2	&0	&107	&0	&0\\  \hline 
%moon	&0	&1	&0	&0	&10	&2	&3	&0	&0	&0	&0	&125	&5\\   \hline 
%callout	&0	&0	&0	&0	&0	&0	&0	&0	&0	&0	&0	&0	&145\\  \hline 
 		\end{tabular}
			}
 		%\end{tabular}
 	%}
	\caption{Confusion Matrix of HS-DB}
	\label{tab:ConfusionMatrix}
	%\end{minipage}
\end{table*}

@@

\subsubsection{Features Comparisons}
\label{sec:featuresComparisions}
Different feature sets are tested to determine the best features that can used in sketch and symbol recognition. Figure\ref{fig:testFeaturesAll} shows the result of different feature sets from the basic four sets (\textbf{FS1,FS2,FS3,FS4}). Result shows that (\textbf{FS2}) Rubine features \cite{gestureexample12} gives the worst results when used alone without any other features. This is because they are mainly computed for single stroke gestures and fare bad in multi-stroke symbols \cite{compareFeaturSVM}. Features \textbf{(FS4)} gives good results but it is improved by adding structural features \textbf{(FS1)}.  Figures \ref{fig:testFeaturesLDDB} and \ref{fig:ELtestFeaturesAll} show similar results on \textsl{EL-DB} and \textsl{LD-DB} dataset. The figures show that on both datasets \textbf{FS1} perform better than on \textsl{HS-DB}, this is a result that shapes in the \textsl{EL-DB} and \textsl{LD-DB} has more structural and conceptual differences than shapes in \textsl{HS-DB}. In \cite{HeloiseBeautification} used Zernike moment (FS3) and mentioned that order higher than 8 yield to little or no improvement. In our system we used much higher order to reach this saturation level. This is due to the level of details in the EL-DB and DL-DB sets.  Result shows that combining feature set FS4 and FS1 gives results compared to moments in both datasets \textsl{EL-DB} and \textsl{LD-DB}.    % achieved  HS-DB a
 \begin{figure}
	\centering
		\includegraphics[scale=0.5]{paperImages/featuresdifference.jpg.eps}
	\caption{Feature Comparison on Hs-DB} The effect of different features on accuracy.  %The graph shows the recognition rate of each symbol using different algorithms. 
	\label{fig:testFeaturesAll}
\end{figure}

@@

 The main features affected by the segmentation stage are the geometric features computed in\textbf{FS1}. Hence those are the features we used to estimate the efficiency of the segmentation algorithm. The recognition accuracy using only the geometrical features is reported in Figure \ref{fig:testFeatonly} . The figure shows that \textsl{AlgS2} achieve better results.  %effect of the segmentation algorithm 
 %Figure \ref{fig:SampleSeg} shows a sample of the output of the segmentation block. The result of segmentation block is tested by their effect on the final recognition results using the features that will be highly affected using different algorithms like \textbf{FS1} and \textbf{FS4} (Section\ref{sec:Recognition}). Figure \ref{fig:testFeatonly} shows the result of the different algorithms using only \textbf{FS1 }features. 
 \begin{figure}
	\centering
		\includegraphics[scale=0.4]{paperImages/featureFS1only.jpg.eps}
	\caption{The effect of segmentation on Hs-DB accuracy} %The effect of symbol complexity.  %The graph shows the recognition rate of each symbol using different algorithms. 
	\label{fig:testFeatonly}
\end{figure}  
% \begin{figure}
%	\centering
%		\includegraphics[scale=0.3]{paperImages/featureFS1only.jpg.eps}
%	\caption{The effect of segmentation on LD-DB accuracy} %The effect of symbol complexity.  %The graph shows the recognition rate of each symbol using different algorithms. 
%	\label{fig:LDtestFeatonly}
%\end{figure}  
 \begin{figure}
	\centering
		\includegraphics[scale=0.8]{results/F1EL.eps}
	\caption{The effect of segmentation on EL-DB accuracy} %The effect of symbol complexity.  %The graph shows the recognition rate of each symbol using different algorithms. 
	\label{fig:ELtestFeatonly}
\end{figure}  
%
% \begin{figure}
%	\centering
%		\includegraphics[scale=0.5]{results/testFeat.eps}
%	\caption{Feature Comparison} The effect of different features on accuracy on \textsl{Hs-DB}.  %The graph shows the recognition rate of each symbol using different algorithms. 
%	\label{fig:testFeaturesAllHS}
%\end{figure}  
%
% \begin{figure}
%	\centering
%		\includegraphics[scale=0.5]{results/testF1.eps}
%	\caption{Feature Comparison} The effect of different features on accuracy on \textsl{MD-DB}.  %The graph shows the recognition rate of each symbol using different algorithms. 
%	\label{fig:testFeaturesAllMD}
%\end{figure}

>>>>

	\caption[Symbols in EL-DB]{Example of Electrical Symbols}
	\label{fig:ElectSet}
\end{figure}
\begin{table}
\begin{center}
\caption[Datasets Comparisons]{Datasets Comparisons} 
\scalebox{0.9}{
 \begin{tabular}{|p{5cm}|p{2.5cm}|p{2.5cm}|p{2.5cm}|}
 \hline
 & Hs-DB &  EL-DB & LD-DB \\ \hline
No of samples  &  7791 & 2764 & 1859 \\ \hline
No of categories  & 13 & 15 & 8 \\ \hline
Avg. Samples per Category& 600 & 184 & 232 \\\hline 
No of users  & 16 & 7 & 7 \\  \hline
Balanced & Yes&No & No \\ \hline
Splits  & 5 random splits  & 5 random splits  & 5 random splits  \\ \hline
Examples & Figure \ref{fig:symbolSet}  & Figure \ref{fig:ElectSet}  & Figure \ref{fig:LogicSet}   \\ \hline
\end{tabular}
}

\label{tab:datasets}

@@

 \begin{table*}
 \caption{Confusion Matrix of HS-DB}
	\centering
	%\small
%	\scalebox{0.7}{
		%	\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|c|c|c|}\hline 
	\scalebox{0.5}{
		\begin{tabular}{|p{2cm}|c|c|c|c|c|c|c|c|c|c|c|c|c||p{2cm}|c|c|c|c|p{2cm}|}\hline 
		Categorie / classified as ==$>$	&ellipse	&heart	&trapezoid	&pentagon	&arch	&hexagon	&square	&triangle	&cube	&cylinder	&parallelogram	&moon	&callout	&Number of samples per class	&TP count	&FP count	&Fn	&Precision	&Recall ( TP rate )\\ \hline 
ellipse	&150	&20	&0	&0	&0	&5	&1	&0	&0	&0	&0	&1	&0	&152	&150	&27	&2	&0.8474	&0.9868\\ \hline 
heart	&2	&130	&0	&1	&10	&1	&1	&0	&0	&0	&1	&4	&0	&152	&130	&20	&22	&0.86666	&0.8552\\ \hline 
trapezoid	&0	&1	&147	&5	&1	&0	&1	&3	&2	&0	&37	&0	&0	&150	&147	&50	&3	&0.7461	&0.98\\ \hline 
pentagon	&0	&0	&1	&139	&0	&7	&0	&0	&0	&0	&1	&0	&0	&152	&139	&9	&13	&0.9391	&0.91447\\ \hline 
arch	&0	&0	&1	&1	&125	&0	&4	&0	&3	&0	&0	&15	&1	&151	&125	&25	&26	&0.83333	&0.82781\\ \hline 
hexagon	&0	&0	&0	&2	&0	&135	&0	&0	&0	&0	&0	&0	&0	&151	&135	&2	&16	&0.9854	&0.89403\\ \hline 
square	&0	&0	&0	&0	&0	&0	&138	&0	&0	&0	&0	&1	&0	&151	&138	&1	&13	&0.9928	&0.91390\\ \hline 
triangle	&0	&0	&1	&2	&5	&0	&1	&148	&0	&0	&4	&7	&0	&151	&148	&20	&3	&0.88095	&0.98013\\ \hline 
cube	&0	&0	&0	&1	&0	&0	&0	&0	&146	&5	&0	&0	&0	&153	&146	&6	&7	&0.96052	&0.95424\\ \hline  
cylinder	&0	&0	&0	&1	&0	&1	&0	&0	&0	&147	&0	&0	&0	&152	&147	&2	&5	&0.98657	&0.967105\\ \hline 
parallelogram	&0	&0	&0	&0	&0	&0	&2	&0	&2	&0	&107	&0	&0	&150	&107	&4	&43	&0.963	&0.71333\\  \hline 
moon	&0	&1	&0	&0	&10	&2	&3	&0	&0	&0	&0	&125	&5	&153	&125	&21	&28	&0.8561	&0.8169\\ \hline  
callout	&0	&0	&0	&0	&0	&0	&0	&0	&0	&0	&0	&0	&145	&151	&145	&0	&6	&1	&0.9602\\  \hline  
% Categories 	&ellipse	&heart	&trapezoid	&pentagon	&arch	&hexagon	&square	&triangle	&cube	&cylinder	&parallelogram	&moon	&callout\\ \hline 
%ellipse	&150	&20	&0	&0	&0	&5	&1	&0	&0	&0	&0	&1	&0\\  \hline 
%heart	&2	&130	&0	&1	&10	&1	&1	&0	&0	&0	&1	&4	&0\\  \hline 
%trapezoid	&0	&1	&147	&5	&1	&0	&1	&3	&2	&0	&37	&0	&0\\  \hline 
%pentagon	&0	&0	&1	&139	&0	&7	&0	&0	&0	&0	&1	&0	&0\\   \hline 
%arch	&0	&0	&1	&1	&125	&0	&4	&0	&3	&0	&0	&15	&1\\   \hline 
%hexagon	&0	&0	&0	&2	&0	&135	&0	&0	&0	&0	&0	&0	&0\\  \hline 
%square	&0	&0	&0	&0	&0	&0	&138	&0	&0	&0	&0	&1	&0\\   \hline 
%triangle	&0	&0	&1	&2	&5	&0	&1	&148	&0	&0	&4	&7	&0\\  \hline 
%cube	&0	&0	&0	&1	&0	&0	&0	&0	&146	&5	&0	&0	&0\\   \hline 
%cylinder	&0	&0	&0	&1	&0	&1	&0	&0	&0	&147	&0	&0	&0\\  \hline 
%parallelogram	&0	&0	&0	&0	&0	&0	&2	&0	&2	&0	&107	&0	&0\\  \hline 
%moon	&0	&1	&0	&0	&10	&2	&3	&0	&0	&0	&0	&125	&5\\   \hline 
%callout	&0	&0	&0	&0	&0	&0	&0	&0	&0	&0	&0	&0	&145\\  \hline 
 		\end{tabular}
			}
 		%\end{tabular}
 	%}

	\label{tab:ConfusionMatrix}
	%\end{minipage}
\end{table*}

@@

\subsubsection{Features Comparisons}
\label{sec:featuresComparisions}
Different feature sets are tested to determine the best features that can use in sketch and symbol recognition. The system computed in total 70 features in four different features sets. The 13 features of \textbf{FS1},  12 Rubine features in \textbf{FS2} and 32 moments features in \textbf{FS3} and 13 features of  \textbf{FS4} where described in details  section \ref{sec:FeatureExtraction}. Figure\ref{fig:testFeaturesAll} shows the result of different feature sets from the basic four sets (\textbf{FS1,FS2,FS3,FS4}). Result shows that (\textbf{FS2}) Rubine features \cite{gestureexample12} gives the worst results when used alone without any other features. This is because they are mainly computed for single stroke gestures and fare bad in multi-stroke symbols \cite{compareFeaturSVM}. Features \textbf{(FS4)} gives good results but it is improved by adding structural features \textbf{(FS1)}.  Figures \ref{fig:testFeaturesLDDB} and \ref{fig:ELtestFeaturesAll} show similar results on \textsl{EL-DB} and \textsl{LD-DB} dataset. The figures show that on both datasets \textbf{FS1} perform better than on \textsl{HS-DB}, this is a result that shapes in the \textsl{EL-DB} and \textsl{LD-DB} has more structural and conceptual differences than shapes in \textsl{HS-DB}. In \cite{HeloiseBeautification} used Zernike moment (FS3) and mentioned that order higher than 8 yield to little or no improvement. In our system we used much higher order to reach this saturation level. This is due to the level of details in the EL-DB and DL-DB sets.  Result shows that combining feature set FS4 and FS1 gives results compared to moments in both datasets \textsl{EL-DB} and \textsl{LD-DB}.    % achieved  HS-DB a

 \begin{figure}
	\centering
		\includegraphics[scale=0.5]{paperImages/featuresdifference.jpg.eps}
	\caption{Feature Comparison on Hs-DB} The effect of different features on accuracy.  %The graph shows the recognition rate of each symbol using different algorithms. 
	\label{fig:testFeaturesAll}
\end{figure}

@@

 The main features affected by the segmentation stage are the geometric features computed in\textbf{FS1}. Hence those are the features we used to estimate the efficiency of the segmentation algorithm. The recognition accuracy using only the geometrical features is reported in Figure \ref{fig:testFeatonly} . The figure shows that \textsl{AlgS2} achieve better results.  %effect of the segmentation algorithm 
 %Figure \ref{fig:SampleSeg} shows a sample of the output of the segmentation block. The result of segmentation block is tested by their effect on the final recognition results using the features that will be highly affected using different algorithms like \textbf{FS1} and \textbf{FS4} (Section\ref{sec:Recognition}). Figure \ref{fig:testFeatonly} shows the result of the different algorithms using only \textbf{FS1 }features. 
 \begin{figure}
	\centering
		\includegraphics[scale=0.4]{paperImages/featureFS1only.jpg.eps}
	\caption{The effect of segmentation on Hs-DB accuracy} %The effect of symbol complexity.  %The graph shows the recognition rate of each symbol using different algorithms. 
	\label{fig:testFeatonly}
\end{figure}  
% \begin{figure}
%	\centering
%		\includegraphics[scale=0.3]{paperImages/featureFS1only.jpg.eps}
%	\caption{The effect of segmentation on LD-DB accuracy} %The effect of symbol complexity.  %The graph shows the recognition rate of each symbol using different algorithms. 
%	\label{fig:LDtestFeatonly}
%\end{figure}  
 \begin{figure}
	\centering
		\includegraphics[scale=0.8]{results/F1EL.eps}
	\caption{The effect of segmentation on EL-DB accuracy} %The effect of symbol complexity.  %The graph shows the recognition rate of each symbol using different algorithms. 
	\label{fig:ELtestFeatonly}
\end{figure}  
%
% \begin{figure}
%	\centering
%		\includegraphics[scale=0.5]{results/testFeat.eps}
%	\caption{Feature Comparison} The effect of different features on accuracy on \textsl{Hs-DB}.  %The graph shows the recognition rate of each symbol using different algorithms. 
%	\label{fig:testFeaturesAllHS}
%\end{figure}  
%
% \begin{figure}
%	\centering
%		\includegraphics[scale=0.5]{results/testF1.eps}
%	\caption{Feature Comparison} The effect of different features on accuracy on \textsl{MD-DB}.  %The graph shows the recognition rate of each symbol using different algorithms. 
%	\label{fig:testFeaturesAllMD}
%\end{figure}  
%Another expirements where conducted to evaluates the worth of an attribute. The worth of each attribute is measured using two different attribure measures. The first is by measuring the gain ratio with respect to the class, where the gain ration is computed as $Gain_{ration}(class,attribute)=\frac{H(class)-H(class|Attribure}{H(Attribute)}$. The second method is using
